Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 Experiments.tex
Minor fixes experiments

We % collected data about
measured the execution time of the pilots and of the AthenaMP % that have been
executed within them, collecting timestamps at % by considering
all stages of the execution. Experiments have been performed % out of production
by % using
submitting NGE's pilots % on
to TITAN's batch queue. Because of TITAN's % batch queue
policies, the turnaround time of each run of our experiments is dominated by
% the time spent on TITAN's queue
queue time. Since we are interested only in the performances of the NGE, we
removed queue time from our statistics.

All the experiments have been performed by % setting
configuring AthenaMP
% in such a way that it uses
to use all the 16 cores % present on
of TITAN's worker nodes.

>>>>

We % collected data about
measured the execution time of the pilots and of the AthenaMP % that have been
executed within them, collecting timestamps at % by considering
all stages of the execution. Experiments have been performed % out of production
by % using
submitting NGE's pilots % on
to Titan's batch queue. Because of Titan's % batch queue
policies, the turnaround time of each run of our experiments is dominated by
% the time spent on TITAN's queue
queue time. Since we are interested only in the performances of the NGE, we
removed queue time from our statistics.

All the experiments have been performed by % setting
configuring AthenaMP
% in such a way that it uses
to use all the 16 cores % present on
of Titan's worker nodes.
